Functions and Graphics
========================================
## Function that counts the number of odd numbers
```{r}
CountsOdd<-function(x){
  Remainder<- vector(length=length(x))
  Remainder <- x%%2
  count <- sum(Remainder)
  return(count)
  }
```

Now we'll test it.  The answer should be 3:
```{r}
CountsOdd(c(3,5,7))
CountsOdd(c(3,5,7,6,2,0))
```

## Function that counts the number of even numbers
```{r}
CountEvens1<- function(x){
 TotalCount<- length(x) #This finds the amount numbers in the vector x.
 Remainder<- vector(length=length(x)) #Generates a vector of the equal length as x.
 Remainder <- x%%2 
 Oddcount <- sum(Remainder) 
 Evencount<- TotalCount-Oddcount # After counting the total odd numbers in the vector, the function will subtract that amount from the total. If a number is not odd, it must be even. Therefore, the numbers not counted must be even.
 return(Evencount)}
```

The answer should be 2:
``` {r}
CountEvens1(c(3,5,7,6,2,0))
```

## This is another function that will count the number of even numbers.
```{r}
 CountEvens2<- function(x){
  x <- x+1 #This changes every odd number to even and every even number to odd.
  #We can then use the odd count function to count the amount of "odd" numbers.
  Remainder<- vector(length=length(x))
Remainder <- x%%2
Evencount <- sum(Remainder)
return(Evencount)
  }
```

The answer should be 2:
``` {r}
CountEvens2(c(3,5,7,6,2,0))
```

## This will calculate hypotenuse of a right angled triangle.
```{r}
hypotenuseLength<- function(a,b) {
asquared <- a^2
bsquared <- b^2
hypotenusesquared <- asquared + bsquared
hypotenuse<- (hypotenusesquared)^(1/2)
return(hypotenuse)
}
```

Test for the hypotenuse function.

* Answer should be 5.
```{r}
hypotenuseLength(3,4)
```

* Answer should be 85.
```{r}
hypotenuseLength(13,84)
```
 
## This is a function that calculates the missing side of triangle using the Law of Cosine. 
```{r}
LawOfCosines<- function(a,b,theta){
asquared <- a^2
bsquared <- b^2
sum <- asquared + bsquared
Cosine <- cos(theta)
abCosine <- a %*% b %*% Cosine
TwoCosine <- 2 %*% abCosine
csquared <- sum - TwoCosine
c <- (csquared)^(1/2)
return(c)
}
```

Test statements:    
* Equalateral triangle.  Answer should be 10.

```{r}
LawOfCosines(5,5,pi/3)
```

* A collapsed triangle. Answer should be 71.
```{r}
LawOfCosines(13,84,0)
```

*Right angled triangle. Answer should be 85.
```{r}
LawOfCosines(13,84,pi/2)
```

## This will calculate the angle of a triangle using the sides of the triangle 
```{r}
ThetaFromLengths<-function(a,b,c){
asqred <- a^2
bsqred <- b^2
csqred <- c^2
Sum <- asqred + bsqred - csqred
Divisor<- 2%*%a%*%b
quotient <- Sum/Divisor
angles <- acos(quotient)
return(angles)
}
```

Test again on an equilateral and right angled triangle: 
```{r}
ThetaFromLengths(10,10,10)
pi/3
ThetaFromLengths(3,4,5)
pi/2
```
 
## This function tests the accuracy of ThetaFromLengths
```{r}
testThetaFromLengths <- function(a,b,theta){
Difference<- abs(ThetaFromLengths(a,b,LawOfCosines(a,b,theta) ) -theta) 
return(Difference)
}

```

Here are the test cases:
```{r}
testThetaFromLengths(a=100,b=34,theta=2.412)
```

Graphics
==================

## Black Canvas
```{r}
canvas<- function(min, max){
  plot(1:2, type='n', xlim=c(min,max), ylim=c(min,max))
}
canvas(min=0,max=100) 
```

```{r}
DrawCircle<- function(x,y,r,...){
  angles<- seq(from=0, to=2*pi, length= 1000)
  xpts <- x + r*cos(angles)
  ypts <- y + r*sin(angles)
  polygon(xpts, ypts, asp=1, ...)
}
```

## Overlapping Circles
```{r}
canvas(min=0,max=100)
DrawCircle(17,47,10, border="blue") 
DrawCircle(30,38,10, border="yellow") 
```

## Olympic Symbol
```{r}
 
canvas(min=0,max=100)
DrawCircle(17,47,10, border="blue", lwd=7) 
DrawCircle(30,38,10, border="yellow", lwd=7)   
DrawCircle(44,47,10, border="black", lwd=7)
DrawCircle(58,38,10, border="green", lwd=7) 
DrawCircle(72,47,10, border="red", lwd=7)

```

