# Oct 1, 2013

##Reverse
```{r}
reverser <- function(x){
  rsplit <- strsplit(x, split="")
  reversal <- rsplit[[1]][rev(1:nchar(x))]
  stick<- paste(reversal,collapse="")
  return(stick)
}


```

Test statements:
```{r}
#Test statement here. Should return true or false. 
reverser("vsgsfgs") == "sgfsgsv"
```

##Scrambler
```{r}
scrambler <- function(x){
  rscram<- strsplit(x, split="")
  scram <- rscram[[1]][sample(1:nchar(x))]
  stick<- paste(scram, collapse="")
  return(stick)
}


```

Test statements:
```{r}
#Test statement here. Should return true or false. 
scrambler("egegsegr") 
```

#VowelBleeper
```{r}
VowelBleeper<- function(x){
  asterisks<- gsub("[aeiou]", "*", x)
  return(asterisks)
}
```
Test statements:
```{r}
#Test statement here. Should return true or false. 
VowelBleeper("sgethaerhe") == "sg*th**rh*"
```

#l33t
```{r}
l33t<- function(x){
  Ereplace <- gsub("[e]","3", x)
  Oreplace <- gsub("[o]","0", Ereplace)
  Sreplace <- gsub("[s]","5", Oreplace)
  Greplace <- gsub("[g]","9", Sreplace)
return(Greplace)
  }
```
Test statements:
```{r}
#Test statement here. Should return true or false. 
l33t("sgethaerhe")
```
#Substitution Cypher
```{r}
KEY<-function(word){
  for (k in 1:26){
    word<-gsub(letters[k],k,word)
  }
  return(word)
}
```

```{r}
KEY("key")

```{r}
Cypher<- function(word,key=KEY("key")){
  set.seed(key)
  
   from<-c(letters,LETTERS,"'",".",";",":","/", ",", " ")
  
  to<- sample(from, replace=FALSE)
  to<- paste(to, collapse="")
  from<- paste(from,collapse="")
  substituted <-chartr(from,to,word)
  return(substituted)
}

message<-Cypher("The enemy comes at dawn",)
```

```{r}
ECypher<- function(code,key=KEY("key")){
  set.seed(key)
   from<-c(letters,LETTERS,"'",".",";",":","/", ",", " ")
  
  to<- sample(from, replace=FALSE)
  to<- paste(to, collapse="")
  from<- paste(from,collapse="")
  substituted <-chartr(to,from, code)
  return(substituted)
}

ECypher(message,)
```
